Epwshiftr: incorporating open data of climate change prediction into \vspace{4pt} building performance simulation for future adaptation and mitigation\\

### 2023-06-09 full-paper/paper.tex
paper: address reviewer comments

% add caption for codes
\DeclareNewFloatType{Code}{placement=h, fileext=code, name=Listing}
\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}
\captionsetup[Code]{aboveskip=10pt, belowskip=1pt}

% add a custom float environment for listing in figure format
\DeclareFloatingEnvironment[
    fileext=los,
    listname={List of Listings},
    name=Listing,
    placement=tbhp
]{listing}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{%
    commandchars=\\\{\},
    fontsize=\scriptsize,
    numbers=left,
    numbersep=5pt
}
\newenvironment{Shaded}{\captionof{Code}{} \begin{mdframed}[skipabove=0pt]}{\end{mdframed}}
\mdfsetup{%
    innerleftmargin=3pt,
    innerrightmargin=3pt,
    innertopmargin=3pt,
    innerbottommargin=3pt,
    backgroundcolor=shadecolor
}
% adopted from pandoc
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
Future weather data is a prerequisite for accessing the impacts of climate
change on building energy performance. The Morphing statistical downscaling
method, which utilizes the Global Climate Model (GCM) output, is a relatively
simple and reliable method for future weather data prediction and is widely
used in current research/tools. However, existing weather generators typically
assume a single GCM or can only consider GCMs from the old CMIP (Coupled Model
Intercomparison Project) projects published more than ten years ago. This
paper presents a free, open-source tool called epwshiftr for incorporating
open data from the latest CMIP6 project into EnergyPlus Weather (EPW)
generation using the Morphing method. The focus of this tool is to ease the
burden of the cumbersome data preparation process as much as possible while
providing user-friendly and flexible ways to create future EPWs for worldwide
locations.

@@

Building energy simulation (BES) has become increasingly applied to assess
building performance under climate change and yield a more sustainable and
resilient design \citep{yassaghi2019overview}. Weather files form the boundary
conditions of BES and directly affect the results \citep{bhandari2012evaluation}.
Therefore, it is necessary to use further weather data considering climate
change for the design and performance evaluation of new and existing buildings
\citep{picard2020robustness}.

A rich body of research and development exists on weather generators for
creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
the morphing method, a relatively simple and reliable statistical downscaling
method. It is based on the future climate change data predicted by the Global
Climate Model (GCM) and hourly weather data, usually a typical meteorological
year (TMY). Morphing can capture the average future weather conditions from GCM
while preserving historical weather sequences. Multiple future weather
generators have been developed over the decades to integrate climate change
predictions from CMIP (Coupled Model Intercomparison Project) projects that
cover worldwide locations \citep{jentsch2008climate, troup2016morphing, dickinson2016generating, yassaghi2019overview}. Currently,
CCWorldWeatherGen\citep{jentsch2013transforming}, WeatherShift
\citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
future weather generators widely used in literature. CCWorldWeatherGen provides
a graphical interface based on Microsoft Excel to generate weather files in EPW
format supported by EnergyPlus directly. However, it is based on the A2 climate
scenario from the IPCC Third Assessment Report (TAR) published in 2001. Moreover,
it only utilizes data from a single GCM called HadCM3. Like CCWorldWeatherGen,
WeatherShift and Meteonorm also use morphing to generate EPW files for future
climate. They consider two representative concentration pathway (RCP) emission
scenarios, i.e.~RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
Assessment Report (AR5). At the same time, both are commercial products, and the
weather data under a single climate scenario often cost hundreds of dollars.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ssp} \caption{Scenario design matrix for future climate prediction based on SSP  and RCP in ScenarioMIP\citep{oneill2016scenario}}\label{fig:ssp}
\end{figure}

@@

\begin{listing}
\caption{Install epwshiftr}\label{lst:install}
\includegraphics[width=\columnwidth]{figures/code-install.png}
\end{listing}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/workflow} \caption{The primary process of using epwshiftr to generate EPW files for future weather}\label{fig:workflow}
\end{figure}

@@

The \emph{Query Module} provides an interface utilizing the RESTful API provided by
ESGF and thus is capable of querying all CMIP6 GCM outputs based on various
conditions, providing download links of NetCDF files. The query result will be
processed into a data frame that contains 22 metadata that describes each
output. Also, an output index is generated based on the query and is used to
check the data integrity before extracting climate change data.

Listing 2 demonstrates how to use the \texttt{index\_cmip6\_index} interface from the
\emph{Query Module}.

This snippet will send a query to ESGF to list all available daily outputs for
near-surface air temperature (tas) and relative humidity (hurs) from
AWI-CM-1-1-MR GCM first run (r1i1p1f1) under SSP585 climate scenario from the
ScenarioMIP activity for year 2050 and 2080. Also an output index file named
``cmip6\_index.csv'' will be saved.

\begin{listing}
\caption{Query ScenarioMIP outputs using the Query Module}\label{lst:index}
\includegraphics[width=\columnwidth]{figures/code-index.png}
\end{listing}

@@

Fortunately, CMIP6 requires each NetCDF file generated by GCM to contain
specific global attributes, which can be used to describe the data stored in the
file. Among them, 30 are mandatory and are included in every file. Therefore,
the \emph{Database Module} creates a mapping between the ESGF query output and each
global attribute and manages the original big data of ScenarioMIP GCM climate
change. Since the amount of data to extract from the global attributes in NetCDF
is negligible compared to the total data volume of the time-series matrix, the
computational load is small. It should be pointed out that CMIP6 does not
require a specific calendar format for the time series GCM output. Various
calendars exist, including the standard calendar, proleptic gregorian calendar,
365-day calendar, 366-day calendar, 360-day calendar, etc. Therefore, careful
attention has been paid when converting the time range information obtained from
ESGF and NetCDF files to ensure they are all transformed to the standard
calendar.

@@

Listing \ref{lst:db} demonstrates how to use the \texttt{suumary\_database} interface from the
Database Module to get a summary of NetCDF files downloaded against the CMIP6
output index generated using the \emph{Query Module.} This step is necessary as it maps
the loaded files against index so that epwshiftr knows which case is complete
and can be used for the next step.

\begin{listing}
\caption{Summarize the GCM NetCDF files based on the output index}\label{lst:db}
\includegraphics[width=\columnwidth]{figures/code-db.png}
\end{listing}

@@

When the integrity check has been passed, the next step is to extract the raw
time-series data from GCM NetCDF output files. NetCDF stores data as a
three-dimensional time, longitude, and latitude matrix. Therefore, the data can
be extracted through the target location's geographic location information
(latitude and longitude). However, the global grid from GCMs is often coarse.
The spatial resolution is generally around 50km to 100 km, making obtaining
accurate data of target locations challenging. In addition, the spacing of
longitude and latitude in the global grid is usually different. Currently, no
uniform standard method exists to calculate the distance between two points on a
global grid. The common methods are: (a) Euler distance method, (b) Tunnel
Distance method and (c) K-D tree algorithm. The Data Extraction Module uses the
Euler distance method. Moreover, it also provides parameters to specify the
distance threshold of longitude and latitude on the grid from the target
position and the maximum number of grid points to match. Similarly, all data
extraction processes are implemented in parallel to speed up.

\begin{listing}
\caption{Match the global grid points directly using an EPW file and extract raw GCM data}\label{lst:data}
\includegraphics[width=\columnwidth]{figures/code-data.png}
\end{listing}

Listing \ref{lst:data} demonstrates how to use the \texttt{match\_coord} interface from
the \emph{Data Extract Module} to extract all coordinates and data of grid points that
meet the specified requirements, i.e., the maximum geographical distance between
the matched grid points and selected location should be less than 0.5 degree,
and only return the closest point. It also showcases the ability of directly
using an EPW file as input for coordinate matching, as epwshiftr can parse the
geographical information stored in EPW files.

@@

The size of the raw data extracted can be relatively big. For example, based on
the authors' measurements, it takes about 20G memory to read the raw data of 12
climate variables from 2020 to 2100 from 4 climate scenarios and 11 GCMs, which
is often close to, if not greater than, a normal PC's memory. For this reason,
epwshiftr supports storing the original data in the fst format \citep{mark2022fst}
with a super large compression ratio, which greatly reduces the content burden
required for calculation. Still taking the above situation as an example, if the
data is divided by GCM, the size of a single fst file is only about 50MB, which
can be easily read and processed by current mainstream home computers.

@@

@@

Listing \ref{lst:epw} demonstrates how to use the \texttt{morphing\_epw} interface from
the \emph{Morphing Module} and the \texttt{future\_epw} interface from the \emph{EPW Generation
Module} to perform morphing on the baseline EPW data and raw GCM data, and
create future EPW files based on the GCM source, climate scenarios and time
interval. All EPW files will be saved into a seprate folder.

\begin{listing}
\caption{Perform morphing and generate future EPWs}\label{lst:epw}
\includegraphics[width=\columnwidth]{figures/code-epw.png}
\end{listing}

>>>>

% add caption for codes
\DeclareNewFloatType{code}{placement=h, fileext=code, name=Listing}
\captionsetup[code]{aboveskip=10pt, belowskip=1pt}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{%
    commandchars=\\\{\},
    fontsize=\normalsize,
    numbers=left,
    numbersep=5pt
}

\newenvironment{Shaded}{\begin{mdframed}[skipabove=0pt]}{\end{mdframed}}
\mdfsetup{%
    innerleftmargin=3pt,
    innerrightmargin=3pt,
    innertopmargin=3pt,
    innerbottommargin=3pt,
    backgroundcolor=shadecolor
}
% adopted from pandoc
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
%-----------------------------SET FONTS -------------------------------------------------------------------
% Set fonts for title, section and subsection headings
\makeatletter
\renewcommand\title[1]{\gdef\@title{\fontsize{12pt}{2pt}\bfseries{#1}}}
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}{3pt}{3pt}{\normalfont\large\bfseries}}
% \normalfont\large
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{\z@}{\normalfont\normalsize\bfseries}}
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{1}{\z@}{\z@}{0.1pt}{\normalfont\normalsize\bfseries}}
\renewcommand\refname{References}
%END OF THE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
Future weather data is a prerequisite for accessing the impacts of climate
change on building energy performance. The Morphing statistical downscaling
method, which utilizes the Global Climate Model (GCM) output, is a relatively
simple method for future weather data prediction and is widely
used in current research/tools. However, existing weather generators typically
assume a single GCM or can only consider GCMs from the old CMIP (Coupled Model
Intercomparison Project) projects published more than ten years ago. This
paper presents a free, open-source tool called epwshiftr for incorporating
open data from the latest CMIP6 project into EnergyPlus Weather (EPW)
generation using the Morphing method. The focus of this tool is to ease the
burden of the cumbersome data preparation process as much as possible while
providing user-friendly and flexible ways to create future EPWs for worldwide
locations.

@@

Building energy simulation (BES) has become increasingly applied to assess
building performance under climate change and yield a more sustainable and
resilient design \citep{yassaghi2019overview}. Weather files form the boundary
conditions of BES and directly affect the results \citep{bhandari2012evaluation}.
Therefore, it is necessary to use future weather data considering climate
change for the design and performance evaluation of new and existing buildings
\citep{picard2020robustness}.

A rich body of research and development exists on weather generators for
creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
the morphing method, a relatively simple statistical downscaling
method. It is based on the future climate change data predicted by the Global
Climate Model (GCM) and hourly weather data, usually a typical meteorological
year (TMY). Morphing can capture the average future weather conditions from GCM
while preserving historical weather sequences. It requires low computational
power, making it possible to create many weather files from worldwide locations.
However, morphing may under- or overestimate climate change impacts because of
the lacking of ability to capture future extreme weather conditions and
potential differences in the reference time frame of the TMY and GCM data
\citep{moazami2019impacts}.
Moreover, careful consideration should be given to morphing when modifying
individual meteorological variables independently, breaking their physical
relationships. Despite these shortcomings, this method is still widely used
because of its simple and flexible characteristics.
Multiple morphing-based future weather
generators have been developed over the decades to integrate climate change
predictions from CMIP (Coupled Model Intercomparison Project) projects that
cover worldwide locations \citep{jentsch2008climate, troup2016morphing, dickinson2016generating, yassaghi2019overview}. Currently,
CCWorldWeatherGen\citep{jentsch2013transforming}, WeatherShift
\citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
future weather generators widely used in literature. CCWorldWeatherGen provides
a graphical interface based on Microsoft Excel to generate weather files in EPW
format supported by EnergyPlus directly. However, it is based on the A2 climate
scenario from the IPCC Third Assessment Report (TAR) published in 2001. Moreover,
it only utilizes data from a single GCM called HadCM3. Like CCWorldWeatherGen,
WeatherShift and Meteonorm also use morphing to generate EPW files for future
climate. They consider two representative concentration pathway (RCP) emission
scenarios, i.e., RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
Assessment Report (AR5). At the same time, both are commercial products, and the
weather data under a single climate scenario often cost hundreds of dollars.

@@

\begin{figure*}
\includegraphics[width=0.7\textwidth]{figures/ssp-hires} \caption{Scenario design matrix for future climate prediction based on SSP  and RCP in ScenarioMIP\citep{oneill2016scenario}}\label{fig:ssp}
\end{figure*}

@@

\captionof{code}{Install epwshiftr}\label{lst:install}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{install.packages}\NormalTok{(}\StringTok{"epwshiftr"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure*}
\includegraphics[width=0.7\textwidth]{figures/workflow-hires} \caption{The primary process of using epwshiftr to generate EPW files for future weather}\label{fig:workflow}
\end{figure*}

The epwshiftr package follows the Test-Driven Development (TDD) process. Around
450 unit tests are carefully made, covering 94\% of the codebase. They are
automatically run on Windows, macOS, and Linux whenever changes are made in
epwshiftr on CRAN and GitHub.

@@

The \emph{Query Module} provides an interface utilizing the RESTful API provided by
ESGF. It thus is capable of querying all CMIP6 GCM outputs based on various
conditions, providing download links of NetCDF files. The query result will be
processed into a data frame that contains 22 metadata that describes each
output. Also, an output index is generated based on the query to
check the data integrity before extracting climate change data.

Listing \ref{lst:index} demonstrates how to use the \texttt{index\_cmip6\_index}
interface from the \emph{Query Module}.

This snippet will send a query to ESGF to list all available daily outputs for
near-surface air temperature (tas) and relative humidity (hurs) from
AWI-CM-1-1-MR GCM first run (r1i1p1f1) under SSP585 climate scenario from the
ScenarioMIP activity for the year 2050 and 2080. Also, an output index file
named ``cmip6\_index.csv'' will be saved.

\captionof{code}{Query ScenarioMIP outputs using the Query Module}\label{lst:index}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# generate GCM output index}
\NormalTok{idx }\OtherTok{\textless{}{-}} \FunctionTok{init\_cmip6\_index}\NormalTok{(}
  \CommentTok{\# only consider ScenarioMIP activity}
  \AttributeTok{activity =} \StringTok{"ScenarioMIP"}\NormalTok{,}

  \CommentTok{\# output variables of interest}
  \AttributeTok{variable =} \FunctionTok{c}\NormalTok{(}\StringTok{"tas"}\NormalTok{, }\StringTok{"hurs"}\NormalTok{),}

  \CommentTok{\# report frequency}
  \AttributeTok{frequency =} \StringTok{"day"}\NormalTok{,}

  \CommentTok{\# experiment name}
  \AttributeTok{experiment =} \StringTok{"ssp585"}\NormalTok{,}

  \CommentTok{\# GCM name}
  \AttributeTok{source =} \StringTok{"AWI{-}CM{-}1{-}1{-}MR"}\NormalTok{,}

  \CommentTok{\# variant,}
  \AttributeTok{variant =} \StringTok{"r1i1p1f1"}\NormalTok{,}

  \CommentTok{\# years of interest}
  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{),}

  \CommentTok{\# save result as an output index file}
  \AttributeTok{save =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

Fortunately, CMIP6 requires each NetCDF file generated by GCM to contain
specific global attributes, which can be used to describe the data stored in the
file. Among them, 30 are mandatory and are included in every file. Therefore,
the \emph{Database Module} creates a mapping between the ESGF query output and each
global attribute and manages the original big data of ScenarioMIP GCM climate
change. The computational load is small since the amount of data to extract from
the global attributes in NetCDF is negligible compared to the total data volume
of the time-series matrix. It should be pointed out that CMIP6 does not
require a specific calendar format for the time series GCM output. Various
calendars exist, including the standard calendar, proleptic Gregorian calendar,
365-day calendar, 366-day calendar, 360-day calendar, etc. Therefore, careful
attention has been paid when converting the time range information obtained from
ESGF and NetCDF files to ensure they are all transformed into the standard
calendar.

@@

Listing \ref{lst:db} demonstrates how to use the \texttt{suumary\_database} interface from the
Database Module to get a summary of NetCDF files downloaded against the CMIP6
output index generated using the \emph{Query Module.} This step is necessary as it maps
the loaded files against the index so that epwshiftr knows which case is
complete and can be used for the next step.

\captionof{code}{Summarize the GCM NetCDF files based on the output index}\label{lst:db}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sm }\OtherTok{\textless{}{-}} \FunctionTok{summary\_database}\NormalTok{(}
  \CommentTok{\# where all the NetCDF files are}
  \AttributeTok{dir =} \FunctionTok{getOption}\NormalTok{(}\StringTok{"epwshiftr.dir"}\NormalTok{),}

  \CommentTok{\# criteria for calculating completeness}
  \AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"source"}\NormalTok{, }\StringTok{"variable"}\NormalTok{),}

  \CommentTok{\# what to do for duplications}
  \AttributeTok{mult =} \StringTok{"latest"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

When the integrity check has been passed, the next step is to extract the raw
time-series data from GCM NetCDF output files. NetCDF stores data as a
three-dimensional time, longitude, and latitude matrix. Therefore, the data can
be extracted through the target location's geographic location information
(latitude and longitude). However, the global grid from GCMs is often coarse.
The spatial resolution is generally around 50km to 100 km, making obtaining
accurate data of target locations challenging. In addition, the spacing of
longitude and latitude in the global grid is usually different. Currently, no
uniform standard method exists to calculate the distance between two points on a
global grid. The common methods are: (a) the Euler distance method, (b) the Tunnel
Distance method, and (c) the K-D tree algorithm. The Data Extraction Module uses the
Euler distance method. Moreover, it also provides parameters to specify the
distance threshold of longitude and latitude on the grid from the target
position and the maximum number of grid points to match. Similarly, all data
extraction processes are implemented in parallel to speed up.

Listing \ref{lst:data} demonstrates how to use the \texttt{match\_coord} interface from
the \emph{Data Extract Module} to extract all coordinates and data of grid points that
meet the specified requirements, i.e., the maximum geographical distance between
the matched grid points and selected location should be less than 0.5 degrees,
and only return the closest point. It also showcases the ability to directly
use an EPW file as input for coordinate matching, as epwshiftr can parse the
geographical information stored in EPW files.

@@

\captionof{code}{Match the global grid points directly using an EPW file and  extract raw GCM data}\label{lst:data}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# use weather file distributed from}
\CommentTok{\# EnergyPlus v8.8 as an example}
\NormalTok{epw }\OtherTok{\textless{}{-}}\NormalTok{ eplusr}\SpecialCharTok{::}\FunctionTok{path\_eplus\_weather}\NormalTok{(}
  \AttributeTok{ver =} \FloatTok{8.8}\NormalTok{,}
  \AttributeTok{file =} \StringTok{"USA\_CA\_San.Francisco.Intl.AP.724940\_TMY3.epw"}
\NormalTok{)}

\CommentTok{\# extract matched grid coordinates}
\NormalTok{coord }\OtherTok{\textless{}{-}} \FunctionTok{match\_coord}\NormalTok{(}
\NormalTok{  epw,}

  \CommentTok{\# match distance less than 0.5 degrees}
  \AttributeTok{threshold =} \FunctionTok{list}\NormalTok{(}\AttributeTok{lon =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{lat =} \FloatTok{0.5}\NormalTok{),}

  \CommentTok{\# match at most 3 grid points}
  \AttributeTok{max\_num =} \DecValTok{3}
\NormalTok{)}

\CommentTok{\# extract all data from matched grid points}
\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{extract\_data}\NormalTok{(coord,}
  \CommentTok{\# specify the years to extract}
  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The size of the raw data extracted can be relatively big. For example, based on
the authors' measurements, it takes about 20G memory to read the raw data of 12
climate variables from 2020 to 2100 from 4 climate scenarios and 11 GCMs, which
is often close to, if not greater than, a typical PC's memory. For this reason,
epwshiftr supports storing the original data in the \emph{fst} format \citep{mark2022fst}
with a super large compression ratio, greatly reducing the content burden
required for calculation. Still taking the above situation as an example, if the
data is divided by GCM, the size of a single fst file is only about 50MB, which
can be easily read and processed by current mainstream home computers.

@@

To avoid unrealistic results, the \emph{Morphing Module} has taken extra data
validation and calculation steps, including but not limited to:

\begin{itemize}
\tightlist
\item
  Warnings are generated if there are any missing values in the input EPW and
  GCM data.
\item
  Unit conversions between data of EPW and GCM are automatically performed using
  the units \citep{pebesma2016measurement} R package, e.g.~all temperature data have
  been converted to Celsius before calculation.
\item
  Calculation of dew point temperature is performed based on dry-bulb
  temperature and relative humidity using the psychrolib \citep{meyer2019psychrolib}
  R package.
\item
  Input values of relative humidity that exceed 100\% will be reset to 100\%.
\item
  A threshold value is set for the stretch factor (\(\alpha\)), i.e.~monthly-mean
  fractional change, when performing morphing operations. The default value is
  set to \texttt{3}. If the absolute \(\alpha\) exceeds this threshold value, warnings
  are issued to suggest users further investigate the input data before
  continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
  to to avoid unrealistic morphed values.
\end{itemize}

Besides the efforts above, the \emph{Morphing Module} always returns the calculated
\(\Delta x\) and \(\alpha\) values in dedicated columns, which provides
opportunities for detailed examination and custom statistical analyses.

@@

Listing \ref{lst:epw} demonstrates how to use the \texttt{morphing\_epw} interface from
the \emph{Morphing Module} and the \texttt{future\_epw} interface from the \emph{EPW Generation
Module} to perform morphing on the baseline EPW data and raw GCM data and
create future EPW files based on the GCM source, climate scenarios and time
interval. All EPW files will be saved into a separate folder.

\captionof{code}{Perform morphing and generate future EPWs}\label{lst:epw}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# perform morphing}
\NormalTok{morphed }\OtherTok{\textless{}{-}} \FunctionTok{morphing\_epw}\NormalTok{(data,}
  \CommentTok{\# years of interest}
  \AttributeTok{years =} \FunctionTok{c}\NormalTok{(}\DecValTok{2050}\NormalTok{, }\DecValTok{2080}\NormalTok{)}
\NormalTok{)}

\CommentTok{\# create future EPWs}
\NormalTok{epws }\OtherTok{\textless{}{-}} \FunctionTok{future\_epw}\NormalTok{(}
\NormalTok{  morphed,}

  \CommentTok{\# how to group the output files}
  \AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"source"}\NormalTok{, }\StringTok{"experiment"}\NormalTok{, }\StringTok{"interval"}\NormalTok{),}

  \CommentTok{\# where to save all generated EPWs}
  \AttributeTok{dir =} \FunctionTok{tempdir}\NormalTok{(),}

  \CommentTok{\# create folders for each group}
  \AttributeTok{separate =} \ConstantTok{TRUE}\NormalTok{,}

  \CommentTok{\# overwrite existing files}
  \AttributeTok{overwrite =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
interface provides parameters to modify which factors should be used for each
meteorological variable, with meaningful defaults value given. For example,
radiation-related variables are, by default, morphed using the stretch factor,
avoiding unrealistic positive values at nighttime. The modular design pattern of
epwshiftr makes it decouple the data structure and the actual extrapolation
algorithm used. We are happy to explore the feasibility of supporting
alternative extrapolation algorithms in the future.
